---
title: "HCAMP Baseline Norms"
output:
  html_document:
    toc: true
    toc_float: true
    theme: spacelab
    highlight: tango 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r, include=FALSE}
library(tidyverse)
library(here)
library(janitor)
library(rio)
library(colorblindr)
library(gghighlight)
library(forcats)
library(ggrepel)
library(gt)
library(knitr)
library(kableExtra)
library(reactable)
library(plotly)
library(glue)
library(fs)
library(rstatix)
library(ggpubr)

theme_set(theme_minimal(15) +
            theme(legend.position = "bottom",
                  panel.grid.major.x = element_line(color = "gray60"),
                  panel.grid.minor.x = element_blank(),
                  panel.grid.major.y = element_blank())
          )


files <- dir_ls(here::here("data"), glob = "*.csv")

d <- map_df(files, read_csv, .id = "file",
                 col_types = cols(.default = "c")) %>% 
  modify(~parse_guess(.x)) %>% 
  janitor::clean_names() %>% 
  mutate(year = parse_number(file)) %>% 
  mutate(year = as.factor(year))

mean_2 <- function(x) {
  z <- na.omit(x)
  sum(z) / length(z)
}

str(d)
d$user_symptom22delayed
d$user_symptom11delayed

impact2 <- d %>% 
  mutate(user_gender = as.factor(user_gender),
         user_age = as.factor(user_age),
         user_handedness = as.factor(user_handedness),
         user_height = as.factor(user_height),
         user_weight = as.factor(user_weight),
         user_country = as.factor(user_country),
         user_first_language = as.factor(user_first_language),
         user_second_language = as.factor(user_second_language),
         user_education_level = as.factor(user_education_level),
         user_special_ed1 = as.factor(user_special_ed1),
         user_special_ed2 = as.factor(user_special_ed2),
         user_special_ed3 = as.factor(user_special_ed3),
         user_special_ed4 = as.factor(user_special_ed4),
         user_special_ed5 = as.factor(user_special_ed5),
         add_adhd = as.factor(add_adhd),
         dyslexia = as.factor(dyslexia),
         autism = as.factor(autism),
         user_treatment_received1 = as.factor(user_treatment_received1),
         user_treatment_received2 = as.factor(user_treatment_received2),
         user_treatment_received3 = as.factor(user_treatment_received3),
         user_treatment_received4 = as.factor(user_treatment_received4),
         user_treatment_received5 = as.factor(user_treatment_received5),
         user_treatment_received6 = as.factor(user_treatment_received6),
         user_treatment_received7 = as.factor(user_treatment_received7),
         user_current_sport = as.factor(user_current_sport),
         user_primary_position = as.factor(user_primary_position),
         user_level_of_participation = as.factor(user_level_of_participation),
         user_years_playing = as.factor(user_years_playing),
         user_number_of_concussions = as.factor(user_number_of_concussions),
         user_concussion_type1 = as.factor(user_concussion_type1),
         user_concussion_type2 = as.factor(user_concussion_type2),
         user_concussion_type3 = as.factor(user_concussion_type3),
         user_concussion_type4 = as.factor(user_concussion_type4),
         user_total_games_missed = as.factor(user_total_games_missed),
         user_concussion_history = as.factor(user_concussion_history),
         user_last_concussion_date = as.factor(user_last_concussion_date),
         test_type = as.factor(test_type),
         test_date = as.factor(test_date),
         exam_language = as.factor(exam_language),
         test_version = as.factor(test_version),
         word_memory_lp = as.factor(word_memory_lp),
         word_memory_dm_correct = as.factor(word_memory_dm_correct),
         word_memory_total_percent_correct = as.factor(word_memory_total_percent_correct),
         design_memory_lp = as.factor(design_memory_lp),
         design_memory_dm_correct = as.factor(design_memory_dm_correct),
         design_memory_total_percent_correct = as.factor(design_memory_total_percent_correct),
         x_oaverage_incorrect = as.factor(x_oaverage_incorrect),
         three_letters_percentage_letters_correct = as.factor(three_letters_percentage_letters_correct),
         user_symptom1delayed = as.factor(user_symptom1delayed))

str(impact2)

impact2$user_symptom1delayed


impact3 <- impact2 %>% 
  mutate(user_age = as.numeric(user_age),
    user_height = as.numeric(user_height),
         user_weight = as.numeric(user_weight),
         user_education_level = as.numeric(user_education_level),
         user_years_playing = as.numeric(user_years_playing),
         user_number_of_concussions = as.numeric(user_number_of_concussions),
         user_concussion_type1 = as.numeric(user_concussion_type1),
         user_concussion_type2 = as.numeric(user_concussion_type2),
         user_concussion_type3 = as.numeric(user_concussion_type3),
         user_concussion_type4 = as.numeric(user_concussion_type4),
         user_total_games_missed = as.numeric(user_total_games_missed),
         word_memory_lp = as.numeric(word_memory_lp),
         word_memory_dm_correct = as.numeric(word_memory_dm_correct),
         word_memory_total_percent_correct = as.numeric(word_memory_total_percent_correct),
         design_memory_lp = as.numeric(design_memory_lp),
         design_memory_dm_correct = as.numeric(design_memory_dm_correct),
         design_memory_total_percent_correct = as.numeric(design_memory_total_percent_correct),
         x_oaverage_incorrect = as.numeric(x_oaverage_incorrect),
         three_letters_percentage_letters_correct = as.numeric(three_letters_percentage_letters_correct),
         user_symptom1delayed = as.numeric(user_symptom1delayed))

str(impact3)

mean_2(impact3$user_symptom1delayed)
mean_2(impact3$user_symptom2delayed)

impact <- impact3

str(impact)

norms <- impact %>% 
  select(passport_id, 
         year,
         test_type,
         user_age, 
         user_gender,
         user_current_sport,
         user_memory_composite_score_verbal,
         user_memory_composite_score_visual,
         user_visual_motor_composite_score,
         user_impulse_control_composite_score,
         user_reaction_time_composite_score) %>% 
  rename(age = user_age,
         gender = user_gender,
         sport = user_current_sport,
         verbal_memory = user_memory_composite_score_verbal,
         visual_memory = user_memory_composite_score_visual,
         visual_motor = user_visual_motor_composite_score,
         impulse_control = user_impulse_control_composite_score,
         reaction_time = user_reaction_time_composite_score)

norms <- norms %>% 
  filter(test_type == "Baseline")

norms <- norms %>% 
  na.omit()

norms_age_range <- norms %>% 
  filter(age >= 12 & age <= 18)

norms_age_range %>% 
  count(age)

norms %>% 
  count(age)

```

# Test Background Information {.tabset .tabset-fade .tabset-pills}

```{r, include=FALSE}
total_all <- norms %>% 
  summarize(length(passport_id))

total_age_range <- norms_age_range %>% 
  summarize(length(passport_id))

total_sum <- data.frame("Level" = c("All Baseline Tests", "Baseline Tests Ages 12-18"), "Total" = c(83998, 79481))

```

## Total Tests

```{r, include=TRUE}
total_sum %>% 
  reactable(columns = list(
    Level = colDef(name = "Level"),
    Total = colDef(name = "Total", 
                   format = colFormat(separators = TRUE, suffix = " individuals"))),
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE)
```

## Age Distribution 

```{r, include=FALSE}
age_tbl <- norms_age_range %>% 
  group_by(age) %>% 
  summarize(total = n()) %>% 
  na.omit() %>% 
  reactable(
    columns = list(
      age = colDef(name = "Age"),
      total = colDef(name = "Total",
                     format = colFormat(separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE
  )

```

```{r, include=TRUE}
age_tbl
```

## Gender Distribution 
```{r, include=FALSE}
gender_tbl <- norms_age_range %>% 
  group_by(gender, age) %>% 
  summarize(total = n()) %>% 
  na.omit() %>% 
  reactable(
    columns = list(
      gender = colDef(name = "Gender"),
      age = colDef(name = "Age"),
      total = colDef(name = "Total",
                     format = colFormat(separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE
  )

gender_tbl
```

```{r, include=TRUE}
gender_tbl
```

## Sport Distribution 

```{r, include=FALSE}
norms_age_range %>% 
  count(sport)

sport_tbl <- norms_age_range %>% 
  group_by(sport) %>% 
  summarize(total = n()) %>% 
  arrange(desc(total)) %>% 
  na.omit() %>% 
  reactable(
    columns = list(
      sport = colDef(name = "Sport"),
      total = colDef(name = "Total",
                     format = colFormat(separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE
  )
```

```{r, include=TRUE}
sport_tbl
```


```{r, include=FALSE}
create_react <- function(df, var) {
    df %>% 
      summarize(Mean = mean({{var}}),
                SD = sd({{var}}),
                Min = min({{var}}),
                Max = max({{var}}),
                Total = length({{var}})) %>% 
      mutate_if(is.numeric, round, 2) %>% 
      reactable(columns = list(
        Mean = colDef(format = colFormat(separators = TRUE)),
        SD = colDef(format = colFormat(separators = TRUE)),
        Min = colDef(format = colFormat(separators = TRUE)),
        Max = colDef(format = colFormat(separators = TRUE)),
        Total = colDef(format = colFormat(separators = TRUE, suffix = " individuals"))
      ))
}

```

# Distribution of Scores by Age (Ages 12-18) {.tabset .tabset-fade .tabset-pills}

```{r, include=FALSE}
age_12 <- norms_age_range %>% 
  filter(age == 12)

age_13 <- norms_age_range %>% 
  filter(age == 13)

age_14 <- norms_age_range %>% 
  filter(age == 14)

age_15 <- norms_age_range %>% 
  filter(age == 15)

age_16 <- norms_age_range %>% 
  filter(age == 16)

age_17_18 <- norms_age_range %>% 
  filter(age == 17 | age == 18)

```

## Age 12 {.tabset .tabset-fade .tabset-pills}

### Verbal Memory 

```{r, include=TRUE}
create_react(age_12, verbal_memory)
```

### Visual Memory

```{r, include=TRUE}
create_react(age_12, visual_memory)
```

### Visual Motor

```{r, include=TRUE}
create_react(age_12, visual_motor)
```

### Impulse Control

```{r, include=TRUE}
create_react(age_12, impulse_control)
```

### Reaction Time

```{r, include=TRUE}
create_react(age_12, reaction_time)
```


## Age 13 {.tabset .tabset-fade .tabset-pills}

### Verbal Memory 

```{r, include=TRUE}
create_react(age_13, verbal_memory)
```

### Visual Memory

```{r, include=TRUE}
create_react(age_13, visual_memory)
```

### Visual Motor

```{r, include=TRUE}
create_react(age_13, visual_motor)
```

### Impulse Control

```{r, include=TRUE}
create_react(age_13, impulse_control)
```

### Reaction Time

```{r, include=TRUE}
create_react(age_13, reaction_time)
```


## Age 14 {.tabset .tabset-fade .tabset-pills}

### Verbal Memory 

```{r, include=TRUE}
create_react(age_14, verbal_memory)
```

### Visual Memory

```{r, include=TRUE}
create_react(age_14, visual_memory)
```

### Visual Motor

```{r, include=TRUE}
create_react(age_14, visual_motor)
```

### Impulse Control

```{r, include=TRUE}
create_react(age_14, impulse_control)
```

### Reaction Time

```{r, include=TRUE}
create_react(age_14, reaction_time)
```


## Age 15 {.tabset .tabset-fade .tabset-pills}

### Verbal Memory 

```{r, include=TRUE}
create_react(age_15, verbal_memory)
```

### Visual Memory

```{r, include=TRUE}
create_react(age_15, visual_memory)
```

### Visual Motor

```{r, include=TRUE}
create_react(age_15, visual_motor)
```

### Impulse Control

```{r, include=TRUE}
create_react(age_15, impulse_control)
```

### Reaction Time

```{r, include=TRUE}
create_react(age_15, reaction_time)
```


## Age 16 {.tabset .tabset-fade .tabset-pills}

### Verbal Memory 

```{r, include=TRUE}
create_react(age_16, verbal_memory)
```

### Visual Memory

```{r, include=TRUE}
create_react(age_16, visual_memory)
```

### Visual Motor

```{r, include=TRUE}
create_react(age_16, visual_motor)
```

### Impulse Control

```{r, include=TRUE}
create_react(age_16, impulse_control)
```

### Reaction Time

```{r, include=TRUE}
create_react(age_16, reaction_time)
```


## Ages 17-18 {.tabset .tabset-fade .tabset-pills}

### Verbal Memory 

```{r, include=TRUE}
create_react(age_17_18, verbal_memory)
```

### Visual Memory

```{r, include=TRUE}
create_react(age_17_18, visual_memory)
```

### Visual Motor

```{r, include=TRUE}
create_react(age_17_18, visual_motor)
```

### Impulse Control

```{r, include=TRUE}
create_react(age_17_18, impulse_control)
```

### Reaction Time

```{r, include=TRUE}
create_react(age_17_18, reaction_time)
```