---
title: "HCAMP Baseline Norms"
output:
  html_document:
    toc: true
    toc_float: true
    theme: spacelab
    highlight: tango 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r, include=FALSE}
library(tidyverse)
library(here)
library(janitor)
library(rio)
library(colorblindr)
library(gghighlight)
library(forcats)
library(ggrepel)
library(gt)
library(knitr)
library(kableExtra)
library(reactable)
library(plotly)
library(glue)
library(fs)
library(rstatix)
library(ggpubr)

theme_set(theme_minimal(15) +
            theme(legend.position = "bottom",
                  panel.grid.major.x = element_line(color = "gray60"),
                  panel.grid.minor.x = element_blank(),
                  panel.grid.major.y = element_blank())
          )


files <- dir_ls(here::here("data"), glob = "*.csv")

d <- map_df(files, read_csv, .id = "file",
                 col_types = cols(.default = "c")) %>% 
  modify(~parse_guess(.x)) %>% 
  janitor::clean_names() %>% 
  mutate(year = parse_number(file)) %>% 
  mutate(year = as.factor(year))

mean_2 <- function(x) {
  z <- na.omit(x)
  sum(z) / length(z)
}

str(d)
d$user_symptom22delayed
d$user_symptom11delayed

impact2 <- d %>% 
  mutate(user_gender = as.factor(user_gender),
         user_age = as.factor(user_age),
         user_handedness = as.factor(user_handedness),
         user_height = as.factor(user_height),
         user_weight = as.factor(user_weight),
         user_country = as.factor(user_country),
         user_first_language = as.factor(user_first_language),
         user_second_language = as.factor(user_second_language),
         user_education_level = as.factor(user_education_level),
         user_special_ed1 = as.factor(user_special_ed1),
         user_special_ed2 = as.factor(user_special_ed2),
         user_special_ed3 = as.factor(user_special_ed3),
         user_special_ed4 = as.factor(user_special_ed4),
         user_special_ed5 = as.factor(user_special_ed5),
         add_adhd = as.factor(add_adhd),
         dyslexia = as.factor(dyslexia),
         autism = as.factor(autism),
         user_treatment_received1 = as.factor(user_treatment_received1),
         user_treatment_received2 = as.factor(user_treatment_received2),
         user_treatment_received3 = as.factor(user_treatment_received3),
         user_treatment_received4 = as.factor(user_treatment_received4),
         user_treatment_received5 = as.factor(user_treatment_received5),
         user_treatment_received6 = as.factor(user_treatment_received6),
         user_treatment_received7 = as.factor(user_treatment_received7),
         user_current_sport = as.factor(user_current_sport),
         user_primary_position = as.factor(user_primary_position),
         user_level_of_participation = as.factor(user_level_of_participation),
         user_years_playing = as.factor(user_years_playing),
         user_number_of_concussions = as.factor(user_number_of_concussions),
         user_concussion_type1 = as.factor(user_concussion_type1),
         user_concussion_type2 = as.factor(user_concussion_type2),
         user_concussion_type3 = as.factor(user_concussion_type3),
         user_concussion_type4 = as.factor(user_concussion_type4),
         user_total_games_missed = as.factor(user_total_games_missed),
         user_concussion_history = as.factor(user_concussion_history),
         user_last_concussion_date = as.factor(user_last_concussion_date),
         test_type = as.factor(test_type),
         test_date = as.factor(test_date),
         exam_language = as.factor(exam_language),
         test_version = as.factor(test_version),
         user_total_symptom_score = as.factor(user_total_symptom_score),
         word_memory_lp = as.factor(word_memory_lp),
         word_memory_dm_correct = as.factor(word_memory_dm_correct),
         word_memory_total_percent_correct = as.factor(word_memory_total_percent_correct),
         design_memory_lp = as.factor(design_memory_lp),
         design_memory_dm_correct = as.factor(design_memory_dm_correct),
         design_memory_total_percent_correct = as.factor(design_memory_total_percent_correct),
         x_oaverage_incorrect = as.factor(x_oaverage_incorrect),
         three_letters_percentage_letters_correct = as.factor(three_letters_percentage_letters_correct),
         user_symptom1delayed = as.factor(user_symptom1delayed))

str(impact2)

impact2$user_symptom1delayed
impact2$user_total_symptom_score


impact3 <- impact2 %>% 
  mutate(user_age = as.numeric(user_age),
    user_height = as.numeric(user_height),
         user_weight = as.numeric(user_weight),
         user_education_level = as.numeric(user_education_level),
         user_years_playing = as.numeric(user_years_playing),
         user_number_of_concussions = as.numeric(user_number_of_concussions),
         user_concussion_type1 = as.numeric(user_concussion_type1),
         user_concussion_type2 = as.numeric(user_concussion_type2),
         user_concussion_type3 = as.numeric(user_concussion_type3),
         user_concussion_type4 = as.numeric(user_concussion_type4),
         user_total_games_missed = as.numeric(user_total_games_missed),
         word_memory_lp = as.numeric(word_memory_lp),
         word_memory_dm_correct = as.numeric(word_memory_dm_correct),
         word_memory_total_percent_correct = as.numeric(word_memory_total_percent_correct),
         design_memory_lp = as.numeric(design_memory_lp),
         design_memory_dm_correct = as.numeric(design_memory_dm_correct),
         design_memory_total_percent_correct = as.numeric(design_memory_total_percent_correct),
         x_oaverage_incorrect = as.numeric(x_oaverage_incorrect),
         three_letters_percentage_letters_correct = as.numeric(three_letters_percentage_letters_correct),
         user_symptom1delayed = as.numeric(user_symptom1delayed),
    user_total_symptom_score = as.numeric(user_total_symptom_score))

str(impact3)

mean_2(impact3$user_symptom1delayed)
mean_2(impact3$user_symptom2delayed)
mean_2(impact3$user_total_symptom_score)

impact <- impact3

str(impact)

norms_all_baseline_tests <- impact %>% 
  select(passport_id, 
         year,
         test_type,
         user_age, 
         user_gender,
         user_current_sport,
         user_memory_composite_score_verbal,
         user_memory_composite_score_visual,
         user_visual_motor_composite_score,
         user_impulse_control_composite_score,
         user_reaction_time_composite_score,
         user_total_symptom_score) %>% 
  rename(age = user_age,
         gender = user_gender,
         sport = user_current_sport,
         verbal_memory = user_memory_composite_score_verbal,
         visual_memory = user_memory_composite_score_visual,
         visual_motor = user_visual_motor_composite_score,
         impulse_control = user_impulse_control_composite_score,
         reaction_time = user_reaction_time_composite_score,
         total_symptom_score = user_total_symptom_score)

norms_all_baseline_tests <- norms_all_baseline_tests %>% 
  filter(test_type == "Baseline")

norms <- norms_all_baseline_tests %>% 
  na.omit()

norms_age_range <- norms %>% 
  filter(age >= 12 & age <= 18)

norms_age_range %>% 
  count(age)

norms %>% 
  count(age)

```

# Test Background Information {.tabset .tabset-fade .tabset-pills}

```{r, include=FALSE}
total_all_missing_included <- norms_all_baseline_tests %>% 
  summarize(length(passport_id))


total_all <- norms %>% 
  summarize(length(passport_id))

total_age_range <- norms_age_range %>% 
  summarize(length(passport_id))

total_sum <- data.frame("Level" = c("Baseline Tests with Missing Scores",
                                    "Baseline Tests with Missing Scores Removed",
                                    "Baseline Tests Ages 12-18"),
                        "Total" = c(85638,
                                    83998,
                                    79481))

```

## Total Tests

Tests with missing scores not included in normed scores below.

```{r, include=TRUE}
total_sum %>% 
  reactable(columns = list(
    Level = colDef(name = "Level"),
    Total = colDef(name = "Total", 
                   format = colFormat(separators = TRUE, suffix = " individuals"))),
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE)
```

## Age Distribution 

```{r, include=FALSE}
age_tbl <- norms_age_range %>% 
  group_by(age) %>% 
  summarize(total = n()) %>% 
  na.omit() %>% 
  reactable(
    columns = list(
      age = colDef(name = "Age"),
      total = colDef(name = "Total",
                     format = colFormat(separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE
  )

```

```{r, include=TRUE}
age_tbl
```

## Gender Distribution 
```{r, include=FALSE}
gender_tbl <- norms_age_range %>% 
  group_by(gender, age) %>% 
  summarize(total = n()) %>% 
  na.omit() %>% 
  reactable(
    columns = list(
      gender = colDef(name = "Gender"),
      age = colDef(name = "Age"),
      total = colDef(name = "Total",
                     format = colFormat(separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE
  )

gender_tbl
```

```{r, include=TRUE}
gender_tbl
```

## Sport Distribution 

```{r, include=FALSE}
norms_age_range %>% 
  count(sport)

sport_tbl <- norms_age_range %>% 
  group_by(sport) %>% 
  summarize(total = n()) %>% 
  arrange(desc(total)) %>% 
  na.omit() %>% 
  reactable(
    columns = list(
      sport = colDef(name = "Sport"),
      total = colDef(name = "Total",
                     format = colFormat(separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE
  )
```

```{r, include=TRUE}
sport_tbl
```

## Sport Distribution by Age

```{r, include=FALSE}
norms_age_range %>% 
  count(sport)

sport_age_tbl <- norms_age_range %>% 
  group_by(sport, age) %>% 
  summarize(total = n()) %>% 
  arrange(desc(total)) %>% 
  na.omit() %>% 
  reactable(
    columns = list(
      sport = colDef(name = "Sport"),
      age = colDef(name = "Age"),
      total = colDef(name = "Total",
                     format = colFormat(separators = TRUE, suffix = " individuals"))),
    pagination = TRUE,
    striped = TRUE,
    outlined = TRUE,
    compact = TRUE,
    highlight = TRUE,
    bordered = TRUE,
    searchable = TRUE
  )
```

```{r, include=TRUE}
sport_age_tbl
```


```{r, include=FALSE}
create_react <- function(df, var) {
    df %>% 
      summarize(Mean = mean({{var}}),
                SD = sd({{var}}),
                Min = min({{var}}),
                Max = max({{var}}),
                Total = length({{var}})) %>% 
      mutate_if(is.numeric, round, 2) %>% 
      reactable(columns = list(
        Mean = colDef(format = colFormat(separators = TRUE)),
        SD = colDef(format = colFormat(separators = TRUE)),
        Min = colDef(format = colFormat(separators = TRUE)),
        Max = colDef(format = colFormat(separators = TRUE)),
        Total = colDef(format = colFormat(separators = TRUE, suffix = " individuals"))
      ))
}

```

# Distribution of Scores by Age (Ages 12-18) {.tabset .tabset-fade .tabset-pills}

```{r, include=FALSE}
age_12 <- norms_age_range %>% 
  filter(age == 12)

age_13 <- norms_age_range %>% 
  filter(age == 13)

age_14 <- norms_age_range %>% 
  filter(age == 14)

age_15 <- norms_age_range %>% 
  filter(age == 15)

age_16 <- norms_age_range %>% 
  filter(age == 16)

age_17_18 <- norms_age_range %>% 
  filter(age == 17 | age == 18)

```

## Age 12 {.tabset .tabset-fade .tabset-pills}

### Verbal Memory 

```{r, include=TRUE}
create_react(age_12, verbal_memory)
```

### Visual Memory

```{r, include=TRUE}
create_react(age_12, visual_memory)
```

### Visual Motor

```{r, include=TRUE}
create_react(age_12, visual_motor)
```

### Impulse Control

```{r, include=TRUE}
create_react(age_12, impulse_control)
```

### Reaction Time

```{r, include=TRUE}
create_react(age_12, reaction_time)
```

### Total Symptom

```{r, include=TRUE}
create_react(age_12, total_symptom_score)
```

## Age 13 {.tabset .tabset-fade .tabset-pills}

### Verbal Memory 

```{r, include=TRUE}
create_react(age_13, verbal_memory)
```

### Visual Memory

```{r, include=TRUE}
create_react(age_13, visual_memory)
```

### Visual Motor

```{r, include=TRUE}
create_react(age_13, visual_motor)
```

### Impulse Control

```{r, include=TRUE}
create_react(age_13, impulse_control)
```

### Reaction Time

```{r, include=TRUE}
create_react(age_13, reaction_time)
```

### Total Symptom

```{r, include=TRUE}
create_react(age_13, total_symptom_score)
```

## Age 14 {.tabset .tabset-fade .tabset-pills}

### Verbal Memory 

```{r, include=TRUE}
create_react(age_14, verbal_memory)
```

### Visual Memory

```{r, include=TRUE}
create_react(age_14, visual_memory)
```

### Visual Motor

```{r, include=TRUE}
create_react(age_14, visual_motor)
```

### Impulse Control

```{r, include=TRUE}
create_react(age_14, impulse_control)
```

### Reaction Time

```{r, include=TRUE}
create_react(age_14, reaction_time)
```

### Total Symptom

```{r, include=TRUE}
create_react(age_14, total_symptom_score)
```

## Age 15 {.tabset .tabset-fade .tabset-pills}

### Verbal Memory 

```{r, include=TRUE}
create_react(age_15, verbal_memory)
```

### Visual Memory

```{r, include=TRUE}
create_react(age_15, visual_memory)
```

### Visual Motor

```{r, include=TRUE}
create_react(age_15, visual_motor)
```

### Impulse Control

```{r, include=TRUE}
create_react(age_15, impulse_control)
```

### Reaction Time

```{r, include=TRUE}
create_react(age_15, reaction_time)
```

### Total Symptom

```{r, include=TRUE}
create_react(age_15, total_symptom_score)
```

## Age 16 {.tabset .tabset-fade .tabset-pills}

### Verbal Memory 

```{r, include=TRUE}
create_react(age_16, verbal_memory)
```

### Visual Memory

```{r, include=TRUE}
create_react(age_16, visual_memory)
```

### Visual Motor

```{r, include=TRUE}
create_react(age_16, visual_motor)
```

### Impulse Control

```{r, include=TRUE}
create_react(age_16, impulse_control)
```

### Reaction Time

```{r, include=TRUE}
create_react(age_16, reaction_time)
```

### Total Symptom

```{r, include=TRUE}
create_react(age_16, total_symptom_score)
```

## Ages 17-18 {.tabset .tabset-fade .tabset-pills}

### Verbal Memory 

```{r, include=TRUE}
create_react(age_17_18, verbal_memory)
```

### Visual Memory

```{r, include=TRUE}
create_react(age_17_18, visual_memory)
```

### Visual Motor

```{r, include=TRUE}
create_react(age_17_18, visual_motor)
```

### Impulse Control

```{r, include=TRUE}
create_react(age_17_18, impulse_control)
```

### Reaction Time

```{r, include=TRUE}
create_react(age_17_18, reaction_time)
```

### Total Symptom

```{r, include=TRUE}
create_react(age_17_18, total_symptom_score)
```

# Distribution of Scores by Age and Gender (Ages 12-18) {.tabset .tabset-fade .tabset-pills}

```{r, include=FALSE}
age_12_girl <- norms_age_range %>% 
  filter(age == 12, 
         gender == "Female")

age_12_boy <- norms_age_range %>% 
  filter(age == 12, 
         gender == "Male")

age_13_girl <- norms_age_range %>% 
  filter(age == 13, 
         gender == "Female")

age_13_boy <- norms_age_range %>% 
  filter(age == 13, 
         gender == "Male")

age_14_girl <- norms_age_range %>% 
  filter(age == 14, 
         gender == "Female")

age_14_boy <- norms_age_range %>% 
  filter(age == 14, 
         gender == "Male")

age_15_girl <- norms_age_range %>% 
  filter(age == 15, 
         gender == "Female")

age_15_boy <- norms_age_range %>% 
  filter(age == 15, 
         gender == "Male")

age_16_girl <- norms_age_range %>% 
  filter(age == 16, 
         gender == "Female")

age_16_boy <- norms_age_range %>% 
  filter(age == 16, 
         gender == "Male")

age_17_18_girl <- norms_age_range %>% 
  filter(age == 17 | age == 18, 
         gender == "Female")

age_17_18_boy <- norms_age_range %>% 
  filter(age == 17 | age == 18, 
         gender == "Male")

```

## Age 12 Female {.tabset .tabset-fade .tabset-pills}

### Verbal Memory

```{r, include=TRUE}
create_react(age_12_girl, verbal_memory)
```

### Visual Memory 

```{r, include=TRUE}
create_react(age_12_girl, visual_memory)
```

### Visual Motor 

```{r, include=TRUE}
create_react(age_12_girl, visual_motor)
```

### Impulse Control 

```{r, include=TRUE}
create_react(age_12_girl, impulse_control)
```

### Reaction Time

```{r, include=TRUE}
create_react(age_12_girl, reaction_time)
```

### Total Symptom

```{r, include=TRUE}
create_react(age_12_girl, total_symptom_score)
```

## Age 12 Male {.tabset .tabset-fade .tabset-pills}

### Verbal Memory

```{r, include=TRUE}
create_react(age_12_boy, verbal_memory)
```

### Visual Memory 

```{r, include=TRUE}
create_react(age_12_boy, visual_memory)
```

### Visual Motor 

```{r, include=TRUE}
create_react(age_12_boy, visual_motor)
```

### Impulse Control 

```{r, include=TRUE}
create_react(age_12_boy, impulse_control)
```

### Reaction Time

```{r, include=TRUE}
create_react(age_12_boy, reaction_time)
```

### Total Symptom

```{r, include=TRUE}
create_react(age_12_boy, total_symptom_score)
```

## Age 13 Female {.tabset .tabset-fade .tabset-pills}

### Verbal Memory

```{r, include=TRUE}
create_react(age_13_girl, verbal_memory)
```

### Visual Memory 

```{r, include=TRUE}
create_react(age_13_girl, visual_memory)
```

### Visual Motor 

```{r, include=TRUE}
create_react(age_13_girl, visual_motor)
```

### Impulse Control 

```{r, include=TRUE}
create_react(age_13_girl, impulse_control)
```

### Reaction Time

```{r, include=TRUE}
create_react(age_13_girl, reaction_time)
```

### Total Symptom

```{r, include=TRUE}
create_react(age_13_girl, total_symptom_score)
```

## Age 13 Male {.tabset .tabset-fade .tabset-pills}

### Verbal Memory

```{r, include=TRUE}
create_react(age_13_boy, verbal_memory)
```

### Visual Memory 

```{r, include=TRUE}
create_react(age_13_boy, visual_memory)
```

### Visual Motor 

```{r, include=TRUE}
create_react(age_13_boy, visual_motor)
```

### Impulse Control 

```{r, include=TRUE}
create_react(age_13_boy, impulse_control)
```

### Reaction Time

```{r, include=TRUE}
create_react(age_13_boy, reaction_time)
```

### Total Symptom

```{r, include=TRUE}
create_react(age_13_boy, total_symptom_score)
```

## Age 14 Female {.tabset .tabset-fade .tabset-pills}

### Verbal Memory

```{r, include=TRUE}
create_react(age_14_girl, verbal_memory)
```

### Visual Memory 

```{r, include=TRUE}
create_react(age_14_girl, visual_memory)
```

### Visual Motor 

```{r, include=TRUE}
create_react(age_14_girl, visual_motor)
```

### Impulse Control 

```{r, include=TRUE}
create_react(age_14_girl, impulse_control)
```

### Reaction Time

```{r, include=TRUE}
create_react(age_14_girl, reaction_time)
```

### Total Symptom

```{r, include=TRUE}
create_react(age_14_girl, total_symptom_score)
```

## Age 14 Male {.tabset .tabset-fade .tabset-pills}

### Verbal Memory

```{r, include=TRUE}
create_react(age_14_boy, verbal_memory)
```

### Visual Memory 

```{r, include=TRUE}
create_react(age_14_boy, visual_memory)
```

### Visual Motor 

```{r, include=TRUE}
create_react(age_14_boy, visual_motor)
```

### Impulse Control 

```{r, include=TRUE}
create_react(age_14_boy, impulse_control)
```

### Reaction Time

```{r, include=TRUE}
create_react(age_14_boy, reaction_time)
```

### Total Symptom

```{r, include=TRUE}
create_react(age_14_boy, total_symptom_score)
```

## Age 15 Female {.tabset .tabset-fade .tabset-pills}

### Verbal Memory

```{r, include=TRUE}
create_react(age_15_girl, verbal_memory)
```

### Visual Memory 

```{r, include=TRUE}
create_react(age_15_girl, visual_memory)
```

### Visual Motor 

```{r, include=TRUE}
create_react(age_15_girl, visual_motor)
```

### Impulse Control 

```{r, include=TRUE}
create_react(age_15_girl, impulse_control)
```

### Reaction Time

```{r, include=TRUE}
create_react(age_15_girl, reaction_time)
```

### Total Symptom

```{r, include=TRUE}
create_react(age_15_girl, total_symptom_score)
```

## Age 15 Male {.tabset .tabset-fade .tabset-pills}

### Verbal Memory

```{r, include=TRUE}
create_react(age_15_boy, verbal_memory)
```

### Visual Memory 

```{r, include=TRUE}
create_react(age_15_boy, visual_memory)
```

### Visual Motor 

```{r, include=TRUE}
create_react(age_15_boy, visual_motor)
```

### Impulse Control 

```{r, include=TRUE}
create_react(age_15_boy, impulse_control)
```

### Reaction Time

```{r, include=TRUE}
create_react(age_15_boy, reaction_time)
```

### Total Symptom

```{r, include=TRUE}
create_react(age_15_boy, total_symptom_score)
```

## Age 16 Female {.tabset .tabset-fade .tabset-pills}

### Verbal Memory

```{r, include=TRUE}
create_react(age_16_girl, verbal_memory)
```

### Visual Memory 

```{r, include=TRUE}
create_react(age_16_girl, visual_memory)
```

### Visual Motor 

```{r, include=TRUE}
create_react(age_16_girl, visual_motor)
```

### Impulse Control 

```{r, include=TRUE}
create_react(age_16_girl, impulse_control)
```

### Reaction Time

```{r, include=TRUE}
create_react(age_16_girl, reaction_time)
```

### Total Symptom

```{r, include=TRUE}
create_react(age_16_girl, total_symptom_score)
```

## Age 16 Male {.tabset .tabset-fade .tabset-pills}

### Verbal Memory

```{r, include=TRUE}
create_react(age_16_boy, verbal_memory)
```

### Visual Memory 

```{r, include=TRUE}
create_react(age_16_boy, visual_memory)
```

### Visual Motor 

```{r, include=TRUE}
create_react(age_16_boy, visual_motor)
```

### Impulse Control 

```{r, include=TRUE}
create_react(age_16_boy, impulse_control)
```

### Reaction Time

```{r, include=TRUE}
create_react(age_16_boy, reaction_time)
```

### Total Symptom

```{r, include=TRUE}
create_react(age_16_boy, total_symptom_score)
```

## Ages 17-18 Female {.tabset .tabset-fade .tabset-pills}

### Verbal Memory

```{r, include=TRUE}
create_react(age_17_18_girl, verbal_memory)
```

### Visual Memory 

```{r, include=TRUE}
create_react(age_17_18_girl, visual_memory)
```

### Visual Motor 

```{r, include=TRUE}
create_react(age_17_18_girl, visual_motor)
```

### Impulse Control 

```{r, include=TRUE}
create_react(age_17_18_girl, impulse_control)
```

### Reaction Time

```{r, include=TRUE}
create_react(age_17_18_girl, reaction_time)
```

### Total Symptom

```{r, include=TRUE}
create_react(age_17_18_girl, total_symptom_score)
```

## Ages 17-18 Male {.tabset .tabset-fade .tabset-pills}

### Verbal Memory

```{r, include=TRUE}
create_react(age_17_18_boy, verbal_memory)
```

### Visual Memory 

```{r, include=TRUE}
create_react(age_17_18_boy, visual_memory)
```

### Visual Motor 

```{r, include=TRUE}
create_react(age_17_18_boy, visual_motor)
```

### Impulse Control 

```{r, include=TRUE}
create_react(age_17_18_boy, impulse_control)
```

### Reaction Time

```{r, include=TRUE}
create_react(age_17_18_boy, reaction_time)
```

### Total Symptom

```{r, include=TRUE}
create_react(age_17_18_boy, total_symptom_score)
```


# Distribution of Scores by Age and Sport (At Least 1,000 Tests Total per Sport Across all Ages) {.tabset .tabset-fade .tabset-pills}

```{r, include=FALSE}
#soccer

soccer <- norms_age_range %>% 
  filter(sport == "Soccer")

soccer_age_12 <- norms_age_range %>% 
  filter(sport == "Soccer",
         age == 12)

soccer_age_13 <- norms_age_range %>% 
  filter(sport == "Soccer",
         age == 13)

soccer_age_14 <- norms_age_range %>% 
  filter(sport == "Soccer",
         age == 14)

soccer_age_15 <- norms_age_range %>% 
  filter(sport == "Soccer",
         age == 15)

soccer_age_16 <- norms_age_range %>% 
  filter(sport == "Soccer",
         age == 16)

soccer_age_17_18 <- norms_age_range %>% 
  filter(sport == "Soccer",
         age == 17 | age == 18)

```

```{r, include=FALSE}
#football

football <- norms_age_range %>% 
  filter(sport == "Football")

football_age_12 <- norms_age_range %>% 
  filter(sport == "Football",
         age == 12)

football_age_13 <- norms_age_range %>% 
  filter(sport == "Football",
         age == 13)

football_age_14 <- norms_age_range %>% 
  filter(sport == "Football",
         age == 14)

football_age_15 <- norms_age_range %>% 
  filter(sport == "Football",
         age == 15)

football_age_16 <- norms_age_range %>% 
  filter(sport == "Football",
         age == 16)

football_age_17_18 <- norms_age_range %>% 
  filter(sport == "Football",
         age == 17 | age == 18)

```

```{r, include=FALSE}
#all football

all_football <- norms_age_range %>% 
  filter(sport == "Football" |
           sport == "Football Varsity" |
           sport == "Football Junior Varsity" |
           sport == "Football Freshman")

all_football_age_12 <- norms_age_range %>% 
  filter(sport == "Football" |
           sport == "Football Varsity" |
           sport == "Football Junior Varsity" |
           sport == "Football Freshman",
         age == 12)

all_football_age_13 <- norms_age_range %>% 
  filter(sport == "Football" |
           sport == "Football Varsity" |
           sport == "Football Junior Varsity" |
           sport == "Football Freshman",
         age == 13)

all_football_age_14 <- norms_age_range %>% 
  filter(sport == "Football" |
           sport == "Football Varsity" |
           sport == "Football Junior Varsity" |
           sport == "Football Freshman",
         age == 14)

all_football_age_15 <- norms_age_range %>% 
  filter(sport == "Football" |
           sport == "Football Varsity" |
           sport == "Football Junior Varsity" |
           sport == "Football Freshman",
         age == 15)

all_football_age_16 <- norms_age_range %>% 
  filter(sport == "Football" |
           sport == "Football Varsity" |
           sport == "Football Junior Varsity" |
           sport == "Football Freshman",
         age == 16)

all_football_age_17_18 <- norms_age_range %>% 
  filter(sport == "Football" |
           sport == "Football Varsity" |
           sport == "Football Junior Varsity" |
           sport == "Football Freshman",
         age == 17 | age == 18)

```

```{r, include=FALSE}
#volleyball

volleyball <- norms_age_range %>% 
  filter(sport == "Volleyball")

volleyball_age_12 <- norms_age_range %>% 
  filter(sport == "Volleyball",
         age == 12)

volleyball_age_13 <- norms_age_range %>% 
  filter(sport == "Volleyball",
         age == 13)

volleyball_age_14 <- norms_age_range %>% 
  filter(sport == "Volleyball",
         age == 14)

volleyball_age_15 <- norms_age_range %>% 
  filter(sport == "Volleyball",
         age == 15)

volleyball_age_16 <- norms_age_range %>% 
  filter(sport == "Volleyball",
         age == 16)

volleyball_age_17_18 <- norms_age_range %>% 
  filter(sport == "Volleyball",
         age == 17 | age == 18)

```

```{r, include=FALSE}
#basketball

basketball <- norms_age_range %>% 
  filter(sport == "Basketball")

basketball_age_12 <- norms_age_range %>% 
  filter(sport == "Basketball",
         age == 12)

basketball_age_13 <- norms_age_range %>% 
  filter(sport == "Basketball",
         age == 13)

basketball_age_14 <- norms_age_range %>% 
  filter(sport == "Basketball",
         age == 14)

basketball_age_15 <- norms_age_range %>% 
  filter(sport == "Basketball",
         age == 15)

basketball_age_16 <- norms_age_range %>% 
  filter(sport == "Basketball",
         age == 16)

basketball_age_17_18 <- norms_age_range %>% 
  filter(sport == "Basketball",
         age == 17 | age == 18)

```

```{r, include=FALSE}
#wrestling 

wrestling <- norms_age_range %>% 
  filter(sport == "Wrestling")

wrestling_age_12 <- norms_age_range %>% 
  filter(sport == "Wrestling",
         age == 12)

wrestling_age_13 <- norms_age_range %>% 
  filter(sport == "Wrestling",
         age == 13)

wrestling_age_14 <- norms_age_range %>% 
  filter(sport == "Wrestling",
         age == 14)

wrestling_age_15 <- norms_age_range %>% 
  filter(sport == "Wrestling",
         age == 15)

wrestling_age_16 <- norms_age_range %>% 
  filter(sport == "Wrestling",
         age == 16)

wrestling_age_17_18 <- norms_age_range %>% 
  filter(sport == "Wrestling",
         age == 17 | age == 18)

```

```{r, include=FALSE}
#football varsity

football_varsity <- norms_age_range %>% 
  filter(sport == "Football Varsity")

football_varsity_age_12 <- norms_age_range %>% 
  filter(sport == "Football Varsity",
         age == 12)

football_varsity_age_13 <- norms_age_range %>% 
  filter(sport == "Football Varsity",
         age == 13)

football_varsity_age_14 <- norms_age_range %>% 
  filter(sport == "Football Varsity",
         age == 14)

football_varsity_age_15 <- norms_age_range %>% 
  filter(sport == "Football Varsity",
         age == 15)

football_varsity_age_16 <- norms_age_range %>% 
  filter(sport == "Football Varsity",
         age == 16)

football_varsity_age_17_18 <- norms_age_range %>% 
  filter(sport == "Football Varsity",
         age == 17 | age == 18)

```

```{r, include=FALSE}
#football jv

football_jv <- norms_age_range %>% 
  filter(sport == "Football Junior Varsity")

football_jv_age_12 <- norms_age_range %>% 
  filter(sport == "Football Junior Varsity",
         age == 12)

football_jv_age_13 <- norms_age_range %>% 
  filter(sport == "Football Junior Varsity",
         age == 13)

football_jv_age_14 <- norms_age_range %>% 
  filter(sport == "Football Junior Varsity",
         age == 14)

football_jv_age_15 <- norms_age_range %>% 
  filter(sport == "Football Junior Varsity",
         age == 15)

football_jv_age_16 <- norms_age_range %>% 
  filter(sport == "Football Junior Varsity",
         age == 16)

football_jv_age_17_18 <- norms_age_range %>% 
  filter(sport == "Football Junior Varsity",
         age == 17 | age == 18)

```

```{r, include=FALSE}
#cheerleading 

cheerleading <- norms_age_range %>% 
  filter(sport == "Cheerleading")

cheerleading_age_12 <- norms_age_range %>% 
  filter(sport == "Cheerleading",
         age == 12)

cheerleading_age_13 <- norms_age_range %>% 
  filter(sport == "Cheerleading",
         age == 13)

cheerleading_age_14 <- norms_age_range %>% 
  filter(sport == "Cheerleading",
         age == 14)

cheerleading_age_15 <- norms_age_range %>% 
  filter(sport == "Cheerleading",
         age == 15)

cheerleading_age_16 <- norms_age_range %>% 
  filter(sport == "Cheerleading",
         age == 16)

cheerleading_age_17_18 <- norms_age_range %>% 
  filter(sport == "Cheerleading",
         age == 17 | age == 18)

```

```{r, include=FALSE}
#baseball

baseball <- norms_age_range %>% 
  filter(sport == "Baseball")

baseball_age_12 <- norms_age_range %>% 
  filter(sport == "Baseball",
         age == 12)

baseball_age_13 <- norms_age_range %>% 
  filter(sport == "Baseball",
         age == 13)

baseball_age_14 <- norms_age_range %>% 
  filter(sport == "Baseball",
         age == 14)

baseball_age_15 <- norms_age_range %>% 
  filter(sport == "Baseball",
         age == 15)

baseball_age_16 <- norms_age_range %>% 
  filter(sport == "Baseball",
         age == 16)

baseball_age_17_18 <- norms_age_range %>% 
  filter(sport == "Baseball",
         age == 17 | age == 18)

```

```{r, include=FALSE}
#softball

softball <- norms_age_range %>% 
  filter(sport == "Softball")

softball_age_12 <- norms_age_range %>% 
  filter(sport == "Softball",
         age == 12)

softball_age_13 <- norms_age_range %>% 
  filter(sport == "Softball",
         age == 13)

softball_age_14 <- norms_age_range %>% 
  filter(sport == "Softball",
         age == 14)

softball_age_15 <- norms_age_range %>% 
  filter(sport == "Softball",
         age == 15)

softball_age_16 <- norms_age_range %>% 
  filter(sport == "Softball",
         age == 16)

softball_age_17_18 <- norms_age_range %>% 
  filter(sport == "Softball",
         age == 17 | age == 18)

```

```{r, include=FALSE}
#martial arts

martial_arts <- norms_age_range %>% 
  filter(sport == "Martial Arts")

martial_arts_age_12 <- norms_age_range %>% 
  filter(sport == "Martial Arts",
         age == 12)

martial_arts_age_13 <- norms_age_range %>% 
  filter(sport == "Martial Arts",
         age == 13)

martial_arts_age_14 <- norms_age_range %>% 
  filter(sport == "Martial Arts",
         age == 14)

martial_arts_age_15 <- norms_age_range %>% 
  filter(sport == "Martial Arts",
         age == 15)

martial_arts_age_16 <- norms_age_range %>% 
  filter(sport == "Martial Arts",
         age == 16)

martial_arts_age_17_18 <- norms_age_range %>% 
  filter(sport == "Martial Arts",
         age == 17 | age == 18)

```


```{r, include=FALSE}
#water polo 

water_polo <- norms_age_range %>% 
  filter(sport == "Water Polo")

water_polo_age_12 <- norms_age_range %>% 
  filter(sport == "Water Polo",
         age == 12)

water_polo_age_13 <- norms_age_range %>% 
  filter(sport == "Water Polo",
         age == 13)

water_polo_age_14 <- norms_age_range %>% 
  filter(sport == "Water Polo",
         age == 14)

water_polo_age_15 <- norms_age_range %>% 
  filter(sport == "Water Polo",
         age == 15)

water_polo_age_16 <- norms_age_range %>% 
  filter(sport == "Water Polo",
         age == 16)

water_polo_age_17_18 <- norms_age_range %>% 
  filter(sport == "Water Polo",
         age == 17 | age == 18)

```


## Football {.tabset .tabset-fade .tabset-pills}

Football scores represent all tests coded as "Football", "Varsity Football", "Junior Varsity Football", and "Freshman Football".

### Ages 12-18 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(all_football, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(all_football, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(all_football, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(all_football, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(all_football, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(all_football, total_symptom_score)
```


### Age 12 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(all_football_age_12, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(all_football_age_12, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(all_football_age_12, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(all_football_age_12, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(all_football_age_12, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(all_football_age_12, total_symptom_score)
```


### Age 13 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(all_football_age_13, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(all_football_age_13, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(all_football_age_13, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(all_football_age_13, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(all_football_age_13, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(all_football_age_13, total_symptom_score)
```


### Age 14 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(all_football_age_14, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(all_football_age_14, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(all_football_age_14, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(all_football_age_14, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(all_football_age_14, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(all_football_age_14, total_symptom_score)
```

### Age 15 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(all_football_age_15, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(all_football_age_15, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(all_football_age_15, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(all_football_age_15, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(all_football_age_15, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(all_football_age_15, total_symptom_score)
```

### Age 16 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(all_football_age_16, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(all_football_age_16, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(all_football_age_16, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(all_football_age_16, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(all_football_age_16, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(all_football_age_16, total_symptom_score)
```

### Ages 17-18 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(all_football_age_17_18, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(all_football_age_17_18, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(all_football_age_17_18, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(all_football_age_17_18, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(all_football_age_17_18, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(all_football_age_17_18, total_symptom_score)
```



## Soccer {.tabset .tabset-fade .tabset-pills}

### Ages 12-18 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(soccer, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(soccer, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(soccer, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(soccer, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(soccer, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(soccer, total_symptom_score)
```


### Age 12 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(soccer_age_12, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(soccer_age_12, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(soccer_age_12, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(soccer_age_12, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(soccer_age_12, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(soccer_age_12, total_symptom_score)
```


### Age 13 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(soccer_age_13, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(soccer_age_13, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(soccer_age_13, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(soccer_age_13, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(soccer_age_13, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(soccer_age_13, total_symptom_score)
```


### Age 14 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(soccer_age_14, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(soccer_age_14, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(soccer_age_14, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(soccer_age_14, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(soccer_age_14, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(soccer_age_14, total_symptom_score)
```

### Age 15 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(soccer_age_15, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(soccer_age_15, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(soccer_age_15, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(soccer_age_15, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(soccer_age_15, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(soccer_age_15, total_symptom_score)
```

### Age 16 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(soccer_age_16, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(soccer_age_16, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(soccer_age_16, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(soccer_age_16, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(soccer_age_16, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(soccer_age_16, total_symptom_score)
```

### Ages 17-18 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(soccer_age_17_18, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(soccer_age_17_18, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(soccer_age_17_18, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(soccer_age_17_18, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(soccer_age_17_18, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(soccer_age_17_18, total_symptom_score)
```


## Volleyball {.tabset .tabset-fade .tabset-pills}

### Ages 12-18 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(volleyball, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(volleyball, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(volleyball, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(volleyball, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(volleyball, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(volleyball, total_symptom_score)
```


### Age 12 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(volleyball_age_12, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(volleyball_age_12, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(volleyball_age_12, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(volleyball_age_12, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(volleyball_age_12, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(volleyball_age_12, total_symptom_score)
```


### Age 13 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(volleyball_age_13, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(volleyball_age_13, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(volleyball_age_13, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(volleyball_age_13, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(volleyball_age_13, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(volleyball_age_13, total_symptom_score)
```


### Age 14 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(volleyball_age_14, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(volleyball_age_14, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(volleyball_age_14, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(volleyball_age_14, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(volleyball_age_14, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(volleyball_age_14, total_symptom_score)
```

### Age 15 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(volleyball_age_15, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(volleyball_age_15, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(volleyball_age_15, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(volleyball_age_15, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(volleyball_age_15, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(volleyball_age_15, total_symptom_score)
```

### Age 16 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(volleyball_age_16, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(volleyball_age_16, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(volleyball_age_16, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(volleyball_age_16, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(volleyball_age_16, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(volleyball_age_16, total_symptom_score)
```

### Ages 17-18 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(volleyball_age_17_18, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(volleyball_age_17_18, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(volleyball_age_17_18, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(volleyball_age_17_18, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(volleyball_age_17_18, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(volleyball_age_17_18, total_symptom_score)
```


## Basketball {.tabset .tabset-fade .tabset-pills}

### Ages 12-18 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(basketball, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(basketball, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(basketball, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(basketball, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(basketball, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(basketball, total_symptom_score)
```


### Age 12 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(basketball_age_12, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(basketball_age_12, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(basketball_age_12, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(basketball_age_12, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(basketball_age_12, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(basketball_age_12, total_symptom_score)
```


### Age 13 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(basketball_age_13, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(basketball_age_13, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(basketball_age_13, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(basketball_age_13, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(basketball_age_13, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(basketball_age_13, total_symptom_score)
```


### Age 14 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(basketball_age_14, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(basketball_age_14, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(basketball_age_14, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(basketball_age_14, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(basketball_age_14, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(basketball_age_14, total_symptom_score)
```

### Age 15 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(basketball_age_15, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(basketball_age_15, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(basketball_age_15, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(basketball_age_15, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(basketball_age_15, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(basketball_age_15, total_symptom_score)
```

### Age 16 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(basketball_age_16, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(basketball_age_16, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(basketball_age_16, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(basketball_age_16, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(basketball_age_16, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(basketball_age_16, total_symptom_score)
```

### Ages 17-18 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(basketball_age_17_18, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(basketball_age_17_18, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(basketball_age_17_18, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(basketball_age_17_18, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(basketball_age_17_18, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(basketball_age_17_18, total_symptom_score)
```


## Wrestling {.tabset .tabset-fade .tabset-pills}

### Ages 12-18 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(wrestling, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(wrestling, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(wrestling, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(wrestling, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(wrestling, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(wrestling, total_symptom_score)
```


### Age 12 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(wrestling_age_12, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(wrestling_age_12, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(wrestling_age_12, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(wrestling_age_12, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(wrestling_age_12, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(wrestling_age_12, total_symptom_score)
```


### Age 13 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(wrestling_age_13, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(wrestling_age_13, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(wrestling_age_13, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(wrestling_age_13, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(wrestling_age_13, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(wrestling_age_13, total_symptom_score)
```


### Age 14 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(wrestling_age_14, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(wrestling_age_14, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(wrestling_age_14, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(wrestling_age_14, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(wrestling_age_14, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(wrestling_age_14, total_symptom_score)
```

### Age 15 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(wrestling_age_15, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(wrestling_age_15, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(wrestling_age_15, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(wrestling_age_15, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(wrestling_age_15, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(wrestling_age_15, total_symptom_score)
```

### Age 16 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(wrestling_age_16, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(wrestling_age_16, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(wrestling_age_16, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(wrestling_age_16, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(wrestling_age_16, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(wrestling_age_16, total_symptom_score)
```

### Ages 17-18 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(wrestling_age_17_18, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(wrestling_age_17_18, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(wrestling_age_17_18, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(wrestling_age_17_18, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(wrestling_age_17_18, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(wrestling_age_17_18, total_symptom_score)
```


## Cheerleading {.tabset .tabset-fade .tabset-pills}

### Ages 12-18 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(cheerleading, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(cheerleading, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(cheerleading, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(cheerleading, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(cheerleading, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(cheerleading, total_symptom_score)
```


### Age 12 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(cheerleading_age_12, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(cheerleading_age_12, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(cheerleading_age_12, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(cheerleading_age_12, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(cheerleading_age_12, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(cheerleading_age_12, total_symptom_score)
```


### Age 13 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(cheerleading_age_13, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(cheerleading_age_13, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(cheerleading_age_13, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(cheerleading_age_13, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(cheerleading_age_13, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(cheerleading_age_13, total_symptom_score)
```


### Age 14 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(cheerleading_age_14, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(cheerleading_age_14, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(cheerleading_age_14, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(cheerleading_age_14, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(cheerleading_age_14, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(cheerleading_age_14, total_symptom_score)
```

### Age 15 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(cheerleading_age_15, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(cheerleading_age_15, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(cheerleading_age_15, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(cheerleading_age_15, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(cheerleading_age_15, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(cheerleading_age_15, total_symptom_score)
```

### Age 16 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(cheerleading_age_16, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(cheerleading_age_16, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(cheerleading_age_16, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(cheerleading_age_16, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(cheerleading_age_16, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(cheerleading_age_16, total_symptom_score)
```

### Ages 17-18 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(cheerleading_age_17_18, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(cheerleading_age_17_18, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(cheerleading_age_17_18, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(cheerleading_age_17_18, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(cheerleading_age_17_18, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(cheerleading_age_17_18, total_symptom_score)
```


## Baseball {.tabset .tabset-fade .tabset-pills}

### Ages 12-18 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(baseball, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(baseball, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(baseball, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(baseball, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(baseball, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(baseball, total_symptom_score)
```


### Age 12 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(baseball_age_12, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(baseball_age_12, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(baseball_age_12, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(baseball_age_12, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(baseball_age_12, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(baseball_age_12, total_symptom_score)
```


### Age 13 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(baseball_age_13, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(baseball_age_13, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(baseball_age_13, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(baseball_age_13, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(baseball_age_13, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(baseball_age_13, total_symptom_score)
```


### Age 14 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(baseball_age_14, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(baseball_age_14, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(baseball_age_14, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(baseball_age_14, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(baseball_age_14, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(baseball_age_14, total_symptom_score)
```

### Age 15 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(baseball_age_15, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(baseball_age_15, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(baseball_age_15, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(baseball_age_15, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(baseball_age_15, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(baseball_age_15, total_symptom_score)
```

### Age 16 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(baseball_age_16, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(baseball_age_16, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(baseball_age_16, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(baseball_age_16, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(baseball_age_16, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(baseball_age_16, total_symptom_score)
```

### Ages 17-18 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(baseball_age_17_18, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(baseball_age_17_18, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(baseball_age_17_18, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(baseball_age_17_18, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(baseball_age_17_18, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(baseball_age_17_18, total_symptom_score)
```


## Softball {.tabset .tabset-fade .tabset-pills}

### Ages 12-18 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(softball, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(softball, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(softball, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(softball, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(softball, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(softball, total_symptom_score)
```


### Age 12 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(softball_age_12, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(softball_age_12, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(softball_age_12, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(softball_age_12, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(softball_age_12, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(softball_age_12, total_symptom_score)
```


### Age 13 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(softball_age_13, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(softball_age_13, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(softball_age_13, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(softball_age_13, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(softball_age_13, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(softball_age_13, total_symptom_score)
```


### Age 14 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(softball_age_14, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(softball_age_14, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(softball_age_14, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(softball_age_14, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(softball_age_14, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(softball_age_14, total_symptom_score)
```

### Age 15 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(softball_age_15, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(softball_age_15, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(softball_age_15, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(softball_age_15, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(softball_age_15, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(softball_age_15, total_symptom_score)
```

### Age 16 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(softball_age_16, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(softball_age_16, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(softball_age_16, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(softball_age_16, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(softball_age_16, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(softball_age_16, total_symptom_score)
```

### Ages 17-18 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(softball_age_17_18, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(softball_age_17_18, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(softball_age_17_18, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(softball_age_17_18, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(softball_age_17_18, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(softball_age_17_18, total_symptom_score)
```


## Martial Arts {.tabset .tabset-fade .tabset-pills}

### Ages 12-18 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(martial_arts, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(martial_arts, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(martial_arts, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(martial_arts, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(martial_arts, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(martial_arts, total_symptom_score)
```


### Age 12 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(martial_arts_age_12, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(martial_arts_age_12, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(martial_arts_age_12, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(martial_arts_age_12, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(martial_arts_age_12, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(martial_arts_age_12, total_symptom_score)
```


### Age 13 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(martial_arts_age_13, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(martial_arts_age_13, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(martial_arts_age_13, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(martial_arts_age_13, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(martial_arts_age_13, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(martial_arts_age_13, total_symptom_score)
```


### Age 14 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(martial_arts_age_14, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(martial_arts_age_14, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(martial_arts_age_14, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(martial_arts_age_14, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(martial_arts_age_14, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(martial_arts_age_14, total_symptom_score)
```

### Age 15 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(martial_arts_age_15, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(martial_arts_age_15, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(martial_arts_age_15, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(martial_arts_age_15, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(martial_arts_age_15, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(martial_arts_age_15, total_symptom_score)
```

### Age 16 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(martial_arts_age_16, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(martial_arts_age_16, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(martial_arts_age_16, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(martial_arts_age_16, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(martial_arts_age_16, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(martial_arts_age_16, total_symptom_score)
```

### Ages 17-18 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(martial_arts_age_17_18, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(martial_arts_age_17_18, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(martial_arts_age_17_18, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(martial_arts_age_17_18, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(martial_arts_age_17_18, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(martial_arts_age_17_18, total_symptom_score)
```


## Water Polo {.tabset .tabset-fade .tabset-pills}

### Ages 12-18 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(water_polo, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(water_polo, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(water_polo, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(water_polo, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(water_polo, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(water_polo, total_symptom_score)
```


### Age 12 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(water_polo_age_12, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(water_polo_age_12, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(water_polo_age_12, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(water_polo_age_12, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(water_polo_age_12, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(water_polo_age_12, total_symptom_score)
```


### Age 13 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(water_polo_age_13, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(water_polo_age_13, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(water_polo_age_13, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(water_polo_age_13, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(water_polo_age_13, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(water_polo_age_13, total_symptom_score)
```


### Age 14 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(water_polo_age_14, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(water_polo_age_14, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(water_polo_age_14, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(water_polo_age_14, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(water_polo_age_14, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(water_polo_age_14, total_symptom_score)
```

### Age 15 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(water_polo_age_15, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(water_polo_age_15, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(water_polo_age_15, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(water_polo_age_15, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(water_polo_age_15, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(water_polo_age_15, total_symptom_score)
```

### Age 16 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(water_polo_age_16, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(water_polo_age_16, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(water_polo_age_16, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(water_polo_age_16, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(water_polo_age_16, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(water_polo_age_16, total_symptom_score)
```

### Ages 17-18 {.tabset .tabset-fade .tabset-pills}

#### Verbal Memory 

```{r, include=TRUE}
create_react(water_polo_age_17_18, verbal_memory)
```

#### Visual Memory 

```{r, include=TRUE}
create_react(water_polo_age_17_18, visual_memory)
```

#### Visual Motor 

```{r, include=TRUE}
create_react(water_polo_age_17_18, visual_motor)
```

#### Impulse Control 

```{r, include=TRUE}
create_react(water_polo_age_17_18, impulse_control)
```

#### Reaction Time

```{r, include=TRUE}
create_react(water_polo_age_17_18, reaction_time)
```

#### Total Symptom 

```{r, include=TRUE}
create_react(water_polo_age_17_18, total_symptom_score)
```


# Model Relationship Between Age and Impact Scores {.tabset .tabset-fade .tabset-pills}

Overall, there are significant differences between average scores and the different ages with older ages achieving better scores, but the models do not account for much variance to define a strong relationship between age and score performance. 

```{r, include=TRUE}
model_data <- norms_age_range %>% 
  mutate(age = as.factor(age),
         gender = as.factor(gender),
         sport = as.factor(sport)) %>% 
  filter(sport == "Football" |
           sport == "Football Varsity" |
           sport == "Football Junior Varsity" |
           sport == "Football Freshman" |
           sport == "Soccer" |
           sport == "Volleyball" |
           sport == "Basketball" |
           sport == "Wrestling" |
           sport == "Cheerleading" |
           sport == "Baseball" |
           sport == "Softball" |
           sport == "Martial Arts" |
           sport == "Water Polo")
```

## Verbal Memory 

```{r, include=TRUE}
verbal_memory_age_mod <- lm(verbal_memory ~ age, data = model_data)

summary(verbal_memory_age_mod)
```


## Visual Memory 

```{r, include=TRUE}
visual_memory_age_mod <- lm(visual_memory ~ age, data = model_data)

summary(visual_memory_age_mod)
```


## Visual Motor 

```{r, include=TRUE}
visual_motor_age_mod <- lm(visual_motor ~ age, data = model_data)

summary(visual_motor_age_mod)
```

## Impulse Control

```{r, include=TRUE}
impulse_control_age_mod <- lm(impulse_control ~ age, data = model_data)

summary(impulse_control_age_mod)
```

## Reaction Time 

```{r, include=TRUE}
reaction_time_age_mod <- lm(reaction_time ~ age, data = model_data)

summary(reaction_time_age_mod)
```


# Model Relationship Between Gender and Impact Scores {.tabset .tabset-fade .tabset-pills}

Overall, females score better than males in all test domains except for visual memory. There are significant differences, but the models do not account for much variance. 

## Verbal Memory 

```{r, include=TRUE}
verbal_memory_gender_mod <- lm(verbal_memory ~ gender, data = model_data)

summary(verbal_memory_gender_mod)
```


## Visual Memory 

```{r, include=TRUE}
visual_memory_gender_mod <- lm(visual_memory ~ gender, data = model_data)

summary(visual_memory_gender_mod)
```


## Visual Motor 

```{r, include=TRUE}
visual_motor_gender_mod <- lm(visual_motor ~ gender, data = model_data)

summary(visual_motor_gender_mod)
```

## Impulse Control

```{r, include=TRUE}
impulse_control_gender_mod <- lm(impulse_control ~ gender, data = model_data)

summary(impulse_control_gender_mod)
```

## Reaction Time 

```{r, include=TRUE}
reaction_time_gender_mod <- lm(reaction_time ~ gender, data = model_data)

summary(reaction_time_gender_mod)
```



# Model Relationship Between Age and Gender and Impact Scores {.tabset .tabset-fade .tabset-pills}

Models do not account for much variance, but significant differences in score performance identified. 

## Verbal Memory 

```{r, include=TRUE}
verbal_memory_age_gender_mod <- lm(verbal_memory ~ age + gender, data = model_data)

summary(verbal_memory_age_gender_mod)
```


## Visual Memory 

```{r, include=TRUE}
visual_memory_age_gender_mod <- lm(visual_memory ~ age + gender, data = model_data)

summary(visual_memory_age_gender_mod)
```


## Visual Motor 

```{r, include=TRUE}
visual_motor_age_gender_mod <- lm(visual_motor ~ age + gender, data = model_data)

summary(visual_motor_age_gender_mod)
```

## Impulse Control

```{r, include=TRUE}
impulse_control_age_gender_mod <- lm(impulse_control ~ age + gender, data = model_data)

summary(impulse_control_age_gender_mod)
```

## Reaction Time 

```{r, include=TRUE}
reaction_time_age_gender_mod <- lm(reaction_time ~ age + gender, data = model_data)

summary(reaction_time_age_gender_mod)
```


# Model Relationship Between Sport and Impact Scores {.tabset .tabset-fade .tabset-pills}

## Verbal Memory 

```{r, include=TRUE}
verbal_memory_sport_mod <- lm(verbal_memory ~ sport, data = model_data)

summary(verbal_memory_sport_mod)
```


## Visual Memory 

```{r, include=TRUE}
visual_memory_sport_mod <- lm(visual_memory ~ sport, data = model_data)

summary(visual_memory_sport_mod)
```


## Visual Motor 

```{r, include=TRUE}
visual_motor_sport_mod <- lm(visual_motor ~ sport, data = model_data)

summary(visual_motor_sport_mod)
```

## Impulse Control

```{r, include=TRUE}
impulse_control_sport_mod <- lm(impulse_control ~ sport, data = model_data)

summary(impulse_control_sport_mod)
```

## Reaction Time 

```{r, include=TRUE}
reaction_time_sport_mod <- lm(reaction_time ~ sport, data = model_data)

summary(reaction_time_sport_mod)
```


# Model Relationship Between Age and Sport and Impact Scores {.tabset .tabset-fade .tabset-pills}

## Verbal Memory 

```{r, include=TRUE}
verbal_memory_age_sport_mod <- lm(verbal_memory ~ age +sport, data = model_data)

summary(verbal_memory_age_sport_mod)
```


## Visual Memory 

```{r, include=TRUE}
visual_memory_age_sport_mod <- lm(visual_memory ~ age + sport, data = model_data)

summary(visual_memory_age_sport_mod)
```


## Visual Motor 

```{r, include=TRUE}
visual_motor_age_sport_mod <- lm(visual_motor ~ age + sport, data = model_data)

summary(visual_motor_age_sport_mod)
```

## Impulse Control

```{r, include=TRUE}
impulse_control_age_sport_mod <- lm(impulse_control ~ age + sport, data = model_data)

summary(impulse_control_age_sport_mod)
```

## Reaction Time 

```{r, include=TRUE}
reaction_time_age_sport_mod <- lm(reaction_time ~ age + sport, data = model_data)

summary(reaction_time_age_sport_mod)
```


















































































































































